Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-01-12 docs/manuscript/manuscript.tex
Update survey summary in results

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Design}
Our target population of interest is researchers who have recently published in the field of geography. 
We followed a 4-step procedure to create a sampling frame for our survey that captures this diverse population of researchers and the approaches they use when studying geography.

@@

The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility. 
Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - Human Geography (30.7\%), Physical Geography (29.8\%), Nature and Society (10.1\%), Geographic Methods and GISci (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statistical Methods}
We conduct two statistical analyses of the survey response. 
First, we used descriptive statistical summaries of the participant response to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.

@@

We also examine group-wise differences in each aggregated measure by disciplinary subfield and methodological approach to identify variation across the discipline's many traditions.
This analysis is based on our full sample (\textit{n}=218), but excludes 29 participants who did not provide complete responses to the relevant survey questions.

Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study. 
We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
We also investigate why researchers were unable to reproduce results.

The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
All of the results presented in this paper can be reproduced using the materials in that repository.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Sampling Frame}
Our target population of interest is researchers who have recently published in the field of geography. 
We followed a 4-step procedure to create a sampling frame for our survey that captures this diverse population of researchers and the approaches they use when studying geography.

@@

\subsection*{Survey Instrument}
The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility. 
Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Analytical Approach}
We conduct two statistical analyses of the survey response
\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
First, we used descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.

@@

We also examine group-wise differences in each aggregated measure by disciplinary subfield and methodological approach to identify variation across the discipline's many traditions.

Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
We also investigate why researchers were unable to reproduce results.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
The refusal rate was 3.1 percent.
\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
Of our 218 respondents, \textit{$n_{1}$}=217 (99.5\%) provided information sufficient for our first analysis of geographic researchers' understanding and perception of reproducibility.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
